Plot Figures for McDuffie et al., 2023 (those generated in R)

### 2023-05-12 analysis/Manuscript/Paper_RFigures.Rmd
Update to R figures script

@@

ggsave(plot = p1, filename = 
         file.path(Plots,'Timeseries_global_population.png'),width = 8,height = 5)

@@

ggsave(plot = p2, filename = 
         file.path(Plots,'Timeseries_global_avgMortRate.png'),width = 8,height = 5)

@@

#plot line graph of global total and top 10 countries (for MMM)
Plots <- file.path(getwd(),'analysis','Manuscript','BenMAP','Outputs')

# Processed BenMAP respiratory mortality output files
# from /analysis/Manuscript/BenMAP/Summarizing BenMAP Results.R
countryResults    <- read.csv(paste0(Plots,"/Country Results Summary by Model & Year.csv"))
globalResults     <- read.csv(paste0(Plots,"/Global Results Summary by Model & Year.csv"))
globalResults2.5  <- read.csv(paste0(Plots,"/Global Results Summary by Model & Year 2_5CI.csv"))
globalResults97.5 <- read.csv(paste0(Plots,"/Global Results Summary by Model & Year 97_5CI.csv"))

@@

p1 <-  ggplot(globalResultslong, aes(x=Model.years,y=value,colour=Model,group=Model,linetype=Model))+
        geom_point()+
        geom_line()+
        scale_linetype_manual(values=c(rep("solid",5),"solid","longdash"))+
        scale_colour_manual(values=c(brewer.pal(11,"Spectral")[c(1,4,9:11)],"black","gray"))+
        scale_size_manual(values=c(rep(1,5),1.5,1))+
        xlab("Year")+ylab("Annual Attributable Respiratory-Related Mortality (deaths)")+
        ggtitle('Annual Respiratory-Related Mortality Attributable to an Increase in \nMDA8 Ozone Exposure from a Methane Pulse in 2020')+
        theme_minimal()+
        scale_x_continuous(breaks=seq(2020,2100,10))+
        scale_y_continuous(limits=c(0,18000))
p1
ggsave(plot = p1, filename = 
         file.path(Plots,'Plots/Timeseries_O3Mort_GCMs.png'),width = 8,height = 5)

@@

p5
ggsave(plot = p5, filename = 
         file.path(Plots,paste0('Total_MortMap_',MODEL,'.png')),width = 9,height = 5)
```

## Figures 2b and SXX

@@

ggsave(plot = p, filename = 
         file.path(Plots,paste0('Relative_2020_CombMaps_',MODEL,'.png')),width = 9,height = 15)

ggsave(plot = p5, filename = 
         file.path(Plots,paste0('Relative_2020_DeathsPerCapMaps_',MODEL,'.png')),width = 9,height = 5)
```

## Figure 2c and SX

@@

ggsave(plot = p1, filename = 
         file.path(Plots,'npd_country_bar_discount.png'),width = 10,height = 5)
ggsave(plot = p2, filename = 
         file.path(Plots,'Fig2c.png'),width = 10,height = 5)

>>>>

## Figure S2
Made elsewhere in python

@@

ggsave(plot = p1, filename = 
         file.path(Plots,'FigS3a.png'),width = 8,height = 5)

@@

ggsave(plot = p2, filename = 
         file.path(Plots,'FigS3b.png'),width = 8,height = 5)

@@

#plot line graph of global total and top 10 countries (for MMM)
Plots <- file.path(getwd(),'analysis','Manuscript','Plots')
input <- file.path(getwd(),'analysis','Manuscript','BenMAP','Outputs')

# Processed BenMAP respiratory mortality output files
# from /analysis/Manuscript/BenMAP/Summarizing BenMAP Results.R
countryResults    <- read.csv(paste0(input,"/Country Results Summary by Model & Year.csv"))
globalResults     <- read.csv(paste0(input,"/Global Results Summary by Model & Year.csv"))
globalResults2.5  <- read.csv(paste0(input,"/Global Results Summary by Model & Year 2_5CI.csv"))
globalResults97.5 <- read.csv(paste0(input,"/Global Results Summary by Model & Year 97_5CI.csv"))

@@

p1 <-  ggplot(globalResultslong, aes(x=Model.years,y=value,colour=Model,group=Model,linetype=Model))+
        geom_point()+
        geom_line()+
        scale_linetype_manual(values=c(rep("solid",5),"solid","longdash"))+
        scale_colour_manual(values=c(brewer.pal(11,"Spectral")[c(1,4,9:11)],"black","gray"))+
        scale_size_manual(values=c(rep(1,5),1.5,1))+
        xlab("Year")+ylab("Annual Attributable Respiratory-Related Mortality (deaths)")+
        ggtitle('Annual Respiratory-Related Mortality Attributable to an Increase in \nMDA8 Ozone Exposure from a Methane Pulse in 2020')+
        theme_minimal()+
        scale_x_continuous(breaks=seq(2020,2100,10))+
        scale_y_continuous(limits=c(0,18000))
p1
ggsave(plot = p1, filename = 
         file.path(Plots,'FigS4.png'),width = 8,height = 5)

@@

p5
ggsave(plot = p5, filename = 
         file.path(Plots,paste0('FigS5_',MODEL,'.png')),width = 9,height = 5)
```

## Figures 2b and S6

@@

ggsave(plot = p, filename = 
         file.path(Plots,paste0('FigS6_',MODEL,'.png')),width = 9,height = 15)

ggsave(plot = p5, filename = 
         file.path(Plots,paste0('Fig2b_',MODEL,'.png')),width = 9,height = 5)
```

## Figure 2c and S7

@@

ggsave(plot = p1, filename = 
         file.path(Plots,'FigS7.png'),width = 10,height = 5)
ggsave(plot = p2, filename = 
         file.path(Plots,'Fig2c.png'),width = 10,height = 5)
